[Re] Speed/accuracy trade-off between the habitual and the goal-directed processes

### 2016-01-06 article/viejo_girard_khamassi.tex
Version ready for submission

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Owen Petchey,
      Marco Plebani,
      Frank Pennekamp,
  },
            pdftitle=
{
[Re] Chaos in a long-term experiment with a plankton community
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

\usepackage[
  backend=biber,
%  style=alphabetic,
%  citestyle=numeric
]{biblatex}
\bibliography{article.bib}

@@

% --- Document ----------------------------------------------------------------
\title{[Re] Chaos in a long-term experiment with a plankton community}

    \usepackage{authblk}
                        \author[1]{Owen Petchey}
                    \author[1]{Marco Plebani}
                    \author[1]{Frank Pennekamp}
                            \affil[1]{Institute of Evolutionary Biology and Environmental Studies, University
of Zurich, Zurich, Switzerland}

\date{\vspace{-5mm}
      \sffamily \small \href{mailto:owen.petchey@ieu.uzh.ch}{owen.petchey@ieu.uzh.ch}}

@@

  {\bfseries Received}  Sep, 1, 2015\\
  {\bfseries Accepted}  Sep, 1, 2015\\
  {\bfseries Published} Sep, 1, 2015\\

@@

\begin{rebox}
\sffamily {\bfseries A reference implementation of}
\small
\begin{flushleft}
\begin{itemize}
    \item[→] Benincà, E., Huisman, J., Heerkloss, R., Jöhnk, K.D., Branco, P., Van
Nes, E.H., Scheffer, M. \& Ellner, S.P. (2008) Chaos in a long-term
experiment with a plankton community. Nature, 451, 822--825 DOI:
10.1038/nature06512
  \end{itemize}\par
\end{flushleft}
\end{rebox}

@@

The original paper describes analyses of fluctuations in the abundance
of organisms in a plankton community derived from the Baltic Sea, housed
in a laboratory environment. The length of the time series (samples
every few days for 2,300 days) allowed for analyses revealing that the
observed dynamics exhibited characteristics consistent with chaos
produced by non-linear species interactions. The article concludes that
stability is not required for persistence of complex food webs, and that
long-term prediction of abundances may be fundamentally impossible. The
demonstration of chaotic dynamics and limited forecast horizons (sensu
\textcite{Petchey2015}) is important in the field of ecology, since the
ability to predict dynamics is an open question with considerable
applied importance \textcite{Petchey2015} \textcite{Mouquet2015}.

@@

This reproduction started with the raw data (source given below) and
used information from the original paper, the supplementary information
\href{http://www.nature.com/nature/journal/v451/n7180/extref/nature06512-s1.pdf}{the
Supplement to the Nature paper}, and communications with Elisa Benincà,
who provided for comparison digitised data from the original article,
and Stephen Ellner, who provided code and data used to produce results
in the original paper. Use of this data and code in this reproduction is
indicated below.

\subsection{Scope of the reproduction}\label{scope-of-the-reproduction}

An attempt was made to reproduce the majority of the results in the
original article. Instances where we did not attempt to reproduce a
result are detailed below.

\subsection{The data}\label{the-data}

The data are available as an Excel file supplement to
\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1461-0248.2009.01391.x/abstract}{an
Ecology Letters publication} \textcite{Beninca2009}. The Excel file
contains several datasheets. Two were particularly important, as they
are the source of the raw data (one contains original species
abundances, the one with the nutrient concentrations). We saved these
two datasheets as comma separated value (csv) text files. In the code
associated with this reproduction, these data files are read from the
associated github repository.

Another datasheet in the Ecology Letters supplement contains transformed
variables (we also saved this as csv file, in order to use it in this
reproduction). We also received a dataset direct from Steve Ellner, see
below for details.

The original species abundance data contained errors (e.g., a few
numerica values had a comma in place of a period as the decimal
separator) that suggested that this was not the exact version of the
dataset used in the original article, or that this was the exact
dataset, but with errors corrected.

\subsection{Reproduction environment}\label{reproduction-environment}

The R language and environment for statistical computing and graphics
was used to make the reproduction. Additional R packages required are
specified in the code associated with this reproduction.

The code for this reproduction resides in an R markdown document, as
well as a source file containing some required functions. Some of the
code takes several minutes to run, so an intermediate data file is
provided with results from this code.

@@

\subsection{Population dynamics}\label{population-dynamics}

The reproduced populations dynamics were at least very similar to those
in figure 1b-g of the original publication (figure \ref{fig:dynamics}).
Note that we plot fourth root transformed values, rather than raw
abundances with a y-axis break, as in the original article.

\begin{figure}[htbp]
\centering
\includegraphics{figures/obs_pop_dyn.pdf}
\caption{\label{fig:dynamics}Observed population dynamics.}
\end{figure}

\subsection{Data transformation}\label{data-transformation}

The following transformation steps were used:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Time series shortened to remove long sequences of zeros.
\item
  Interpolation to create equally spaced observations in time series.
\item
  Fourth root transformation.
\item
  Detrending of five of the time series.
\item
  Rescaling to zero mean and unit standard deviation.
\end{enumerate}

The method for selecting the zeros to remove was unclear. In order to
reproduce this step, we removed the same data as in the original study,
by matching to the transformed data with zeros removed in the Ecology
Letters supplement Excel file mentioned above. All remaining
transformation steps were performed independently of this dataset. Our
reproduction of the transformed data closely matched the published
transformed data.

The data received directly from Stephen Ellner was interpolated, but
without zeros removed. Our interpolated data, without zeros removed,
matched closely this data.

\subsection{Correlations among species
abundances}\label{correlations-among-species-abundances}

Correlations among species abundances presented in Table 1 of the
original article closely matched our reproduced correlations, calculated
from the transformed data with zeros removed (figure
\ref{fig:corr_comp}). Deviations between the original and reproduced
correlations are relatively small (less than 0.072 units) and
infrequent.

\begin{figure}[htbp]
\centering
\includegraphics{figures/correlation_comparison.pdf}
\caption{\label{fig:corr_comp}Comparison of calculated correlations
among species abundances in the original article and this reproduction.}
\end{figure}

Highlighted in the text of the original paper were: negative
correlations of picophytoplankton with protozoa, and of
nanophytoplankton both with rotifers and calanoid copepods, positive
correlation of picophytoplankton with calanoid copepods, negative
correlation between bacteria and ostracods, and positive correlation
between bacteria and phosphorus. All of these correlations were
qualitatively reproduced.

\subsection{Spectral analyses}\label{spectral-analyses}

Spectral analyses in the original paper were presented graphically in
figures S3 (raw spectrograms) and S4 (Welch periodograms). These graphs
were, apparently, visually inspected to reveal: ``fluctuations covered a
range of different periodicities'', and ``picophytoplankton, rotifers
and calanoid copepods seemed to fluctuate predominantly with a
periodicity of about 30 days.'' It is unclear how these conclusions were
derived from figures S3 and S4 of the original article. Our reproduced
spectra (not shown here, but code provided) were not quantitatively
identical to the spectra in the original article.

\subsection{Lyapunov exponents by direct
method}\label{lyapunov-exponents-by-direct-method}

Reproduced divergence rates (figure \ref{fig:divergence}) and Lyapunov
exponents (figure \ref{fig:LE_comparison}) were somewhat different from
those in the original article.. The original article states: ``the
distance between initially nearby trajectories increased over time, and
reached a plateau after about 20--30 days''. The reproduced results
appear not inconsistent with this statement, except for one group of
species (Harpacticoids). The original article also stated that the
analyses ``yielded significantly positive Lyapunov exponents of
strikingly similar value for all species (Fig. 3; mean exponent = 0.057
per day, s.d. = 0.005 per day, n = 9)''. Reproduced exponents had very
similar mean value, but had about four times greater standard deviation
(mean = 0.055 and s.d. = 0.019).

\begin{figure}[htbp]
\centering
\includegraphics{figures/div_rate.pdf}
\caption{\label{fig:divergence}Reproduced divergence rates and Lyapunov
exponents (figure 3 in the original article).}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{figures/LE_comparison.pdf}
\caption{\label{fig:LE_comparison}Comparison of Lyapunov exponents,
estimated by direct method, in the original article and this
reproduction.}
\end{figure}

\subsection{Lyapunov exponents by indirect
method}\label{lyapunov-exponents-by-indirect-method}

The original paper reported global Lyapunov exponent calculated via two
modelling approaches (neural network and generalised additive models
{[}GAMs{]}). Only the GAM approach was reproduced, with the assistance
of code donated by Stephen Ellner. The original article obtained a
global Lyapunov exponent of λ=0.08 day-1. The reproduced value was 0.04.
We did not reproduce the bootstrapping used to give confidence intervals
around this estimate.

\subsection{Predictability decay}\label{predictability-decay}

The article stated: ``For short-term forecasts of only a few days, most
species had a high predictability of R2 = 0.70 -- 0.90 (Fig. 2).
However, the predictability of the species was much reduced when
prediction times were extended to 15--30days.'' The reproduced
predictabilities, which were calculated from the GAMs, were consistent
with these qualitative statements, though were quantitatively different
(\ref{fig:prediction_distance}). We did not reproduce the predictability
estimates for linear models.

\begin{figure}[htbp]
\centering
\includegraphics{figures/prediction_distance.pdf}
\caption{\label{fig:prediction_distance}Predictability (correlation
between predicted and observed abundances) and prediction distance
(days) (figure 2 in the original article). Reproducted data in red, and
data from original publication in black.}
\end{figure}

@@

Although we were not able to make a quantitatively accurate reproduction
of all results of the original article, the qualitative results were
largely identical. For example, all Lyapunov exponents estimated by
direct method are positive, as in the original article, consistent with
chaotic dynamics. Quantitative differences may have resulted from
difference in algorithms used. For example,the original used the
\href{http://www.mpipks-dresden.mpg.de/~tisean/}{Tisean software} to
calculate Lyapunov exponents. As this was available from CRAN
\href{http://cran.r-project.org/web/packages/RTisean/index.html}{until
mid 2014} and since it is a bit less well integrated with R, we instead
use the tseriesChaos package \textcite{tseriesChaos}, which in any case
was largely inspired by the TISEAN project. In addition, there may have
been some difference in algorithm parameters, as not all parameters
required by the functions we used were reported in the original ms.
There may also have been some difference in data used for specific
analyses, e.g., data with zeros removed or not, as it was not always
possible to be totally sure the reproduction used exactly the same data
as the original article.

In conclusion, this reproduction supports the general scientific
conclusions of the original article, but also shows how difficult can be
an accurate quantitative reproduction, even in the presence of the
extensive methodological details provided alongside the original
article.

\section{Acknowledgements}\label{acknowledgements}

This reproduction was made as part of the Reproducible Research in
Ecology, Evolution, Behaviour, and Environmental Studies (RREEBES)
Course, lead by Owen Petchey at the University of Zurich. More
information about the course
\href{https://github.com/opetchey/RREEBES/blob/master/README.md}{here}
on github.

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Guillaume Viejo,
      Benoît Girard,
      Mehdi Khamassi,
  },
            pdftitle=
{
[Re] Speed/accuracy trade-off between the habitual and the goal-directed
processes
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

\usepackage[
  backend=biber,
%  style=alphabetic,
%  citestyle=numeric
]{biblatex}
\bibliography{viejo_girard_khamassi.bib}

@@

% --- Document ----------------------------------------------------------------
\title{[Re] Speed/accuracy trade-off between the habitual and the goal-directed
processes}

    \usepackage{authblk}
                        \author[1]{Guillaume Viejo}
                    \author[1]{Benoît Girard}
                    \author[1]{Mehdi Khamassi}
                            \affil[1]{Sorbonne Universités, UPMC Univ Paris 06, CNRS, Institute of Intelligent
Systems and Robotics (ISIR), F-75005 Paris, France}

\date{\vspace{-5mm}
      \sffamily \small \href{mailto:guillaume.viejo@isir.upmc.fr}{guillaume.viejo@isir.upmc.fr}}

@@

  {\bfseries Received}  Nov, 1, 2015\\
  {\bfseries Accepted}  Sep, 1, 2015\\
  {\bfseries Published} Sep, 1, 2015\\

@@

\begin{rebox}
\sffamily {\bfseries A reference implementation of}
\small
\begin{flushleft}
\begin{itemize}
    \item[→] Speed/accuracy trade-off between the habitual and the goal-directed
processes, M. Keramati, A. Dezfouli, P. Payam, PLoS computational
biology, 7, 2011
  \end{itemize}\par
\end{flushleft}
\end{rebox}

@@

This study is a reference implementation of \textcite{keramati} that
proposed an arbitration mechanism between a goal-directed strategy and a
habitual strategy, used to model the behavior of rats in instrumental
conditionning tasks. The habitual strategy is the Kalman Q-Learning from
\textcite{geist}. We replicate the results of the first task i.e.~the
devaluation experiment with two states and two actions. The
implementation is in python with numpy, scipy and matplotlib library.
The authors couldn't provide the original implementation and we are not
aware of others implementations elsewhere.

@@

We used the description of the model from the original article except
for the implementation of the Kalman Q-Learning which we took from
\textcite{geist}. We used the same parameters as the original article
except for the update rate of the transition function \(\phi\), the
initialization of the covariance matrice and an uncentered transform
parameter \(\kappa\) that were not mentionned in the original article.
The largest uncertainty about the model concerned the devaluation
procedure. Besides setting the reward \(r\) to null, the authors stated
that ``For modeling the devaluation of the outcome in the first two
simulations, \(R(S_1, EM)\) is set to -1.'' As this notation
(\(R(S_1, EM)\)) is not defined in the rest of the article, we assumed
that it is \(\hat{R}(S_1, EM)\) updated by equation (14) in the original
article.

The parameters are as follows :

\begin{longtable}[c]{@{}lll@{}}
\toprule
Name & Description & Value\tabularnewline
\midrule
\endhead
\(\sigma\) & Updating rate of the average reward & 0.02\tabularnewline
\(\eta\) & Variance of evolution noise & 0.0001\tabularnewline
\(P_n\) & Variance of observation noise & 0.05\tabularnewline
\(\beta\) & Rate of exploration & 1.0\tabularnewline
\(\rho\) & Update rate of the reward function & 0.1\tabularnewline
\(\gamma\) & Discount factor & 0.95\tabularnewline
\(\tau\) & Time step of graph exploration & 0.08\tabularnewline
depth & Depth of search in graph exploration & 3\tabularnewline
\(\phi\) & Update rate of the transition function & 0.5\tabularnewline
init cov & Initialisaton of covariance matrice & 1.0\tabularnewline
\(\kappa\) & Unscentered transform parameters & 0.1\tabularnewline
\bottomrule
\end{longtable}

We describe the algorithm of our implementation in details. The process
of action selection and reward update are separated for clarity.

\begin{quote}
\begin{quote}
Initialization
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\[Q(s, a)^{Goal-Directed} = \{ 0, \ldots \}\]
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\[Q(s, a)^{Habitual} = \{ 0, \dots \}\]
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\[
\Sigma = \left(
    \begin{array}{*4{c}}
    cov \times \eta &  0 &  \ldots & 0 \\
     0 &  cov \times \eta &  \ldots & \vdots \\
    \vdots &  \ldots &  \ddots & 0 \\
     0 &  \ldots &  0 & cov \times \eta \\     
  \end{array}\right)
\]
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(R(S1, EM) = 1\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\bar{R} = 0\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\hat{R}(s,a) = \{0,\ldots\}\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
Main Loop
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\textbf{FOR}\ i = 1:T\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(s_t = S_0\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(\textbf{IF}\ i = T_{devaluation}\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(R(S1, EM) = 0\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(\hat{R}(S1, EM) = -1\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(\textbf{WHILE}\ s_t \neq S1 \bigwedge a_t \neq EM\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(a_t = \textbf{Selection}(s_t)\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(r_t = R(s_t,a_t)\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(s_{t+1} = transition(s_t, a_t)\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(\textbf{Update}(s_t,a_t, s_{t+1}, r_t)\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
Selection
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\{a_1,\ldots,ai,\ldots\} \leftarrow sort(Q(s_t,a_i))\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(VPI(s_t, a_1) = (Q(s_t,a_2)^{H}-Q(s_t,a_1)^{H})P(Q(s_t,a_1)^{H}<Q(s_t,a_2)^{H}) + \frac{\sigma(s_t,a_t)}{\sqrt{2\pi}} e^{-\frac{(Q(s_t,a_2)^H - Q(s_t,a_1)^H)^2}{2\sigma(s_t,a_t)^2}}\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(VPI(s_t, a_i) = (Q(s_t,a_i)^{H}-Q(s_t,a_1)^{H})P(Q(s_t,a_i)^{H}>Q(s_t,a_1)^{H}) + \frac{\sigma(s_t,a_t)}{\sqrt{2\pi}} e^{-\frac{(Q(s_t,a_1)^H - Q(s_t,a_i)^H)^2}{2\sigma(s_t,a_t)^2}}\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\textbf{FOR}\ i \in \{a_1, a_2,\ldots, a_i, \ldots\}\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(\textbf{IF}\ VPI(s_t, a_i) \geq \tau \bar{R}\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(Q(s_t,a_i) = \hat{R}(s_t,a_i) + \gamma \sum\limits_{s'}p_{T}(\{s,a\}\rightarrow s') \max\limits_{b \in A} Q(s',b)^{Goal-directed}\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(\textbf{ELSE}\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\(Q(s_t,a_i) = Q(s_t,a_i)^{Habitual}\)
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(a_t \leftarrow \textit{SoftMax}(Q(s_t,a), \beta)\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
Update
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\bar{R} = (1-\sigma) \bar{R} + \sigma r_t\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\hat{R}(s_t,a_t) =(1 - \rho) \hat{R} + \rho r_t\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(p_{T}(s_t, a_t, s_{t+1}) = (1 - \phi) p_{T}(s_t, a_t, s_{t+1}) + \phi\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
Specific to Kalman Q-Learning
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\Theta = \{ \theta_j, 0 \geq j \geq 2|S.A|\}\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\check{W} = \{ w_j, 0 \geq j \geq 2|S.A| \}\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\check{R} = \{ \check{r}_j = \theta_j(s_t,a_t) - \gamma \max\limits_{b \in A} \theta_j(s_{t+1},b),\ 0 \geq j \geq 2|S.A|\}\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(r_{predicted} = \sum\limits_{j=0}^{2|S.A|} w_j \check{r}_j\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(P_{\theta_j \check{r}_j} = \sum\limits_{j=0}^{2|S.A|} w_j (\theta_j - Q^{Habitual}_t)(\check{r}_j - r_{predicted})\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(P_{\check{r}_j} = \sum\limits_{j=0}^{2|S.A|} w_j (\check{r}_j - r_{predicted})^2 + P_n\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(K_t = P_{\theta_j \check{r}_j} P_{\check{r}_j}^{-1}\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(\delta_t = r_t - r_{predicted}\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(Q_{t+1}^{Habitual} = Q_{t}^{H} + K_t \delta_t\)
\end{quote}
\end{quote}
\end{quote}

\begin{quote}
\begin{quote}
\begin{quote}
\(P_{t+1}^{H} = P_{t}^{H} - K_t P_{\Sigma_t} K_t^T\)
\end{quote}
\end{quote}
\end{quote}

@@

We only reproduced the results of Figure 3 A, B, G, H in a qualitative
manner. Results are presented in Figure \ref{fig:figure1}. We can
observe the strategy shift (from goal-directed to habitual) after
extensive training around 50 time steps. In the original article, the
strategy shift occurs after 100 time steps.

However we can observe a difference between the probabilities of action
for the goal-directed model. In our implementation,
\[p(s_0, pl) \simeq 0.7\] and \[p(s_0, em) \simeq 0.3\] before
devaluation. In the original article, \[p(s_0, pl) \simeq 0.6\] and
\[p(s_0, em) \simeq 0.4\] Nevertheless, the probabilities of action from
the Kalman Q-Learning after strategy shifting are equivalent.

\begin{figure}[htbp]
\centering
\includegraphics{../code/fig.pdf}
\caption{\label{fig:figure1}A. Value of Precise Information (full lines)
for action press-lever and enter magazine in state \(S_0\) and reward
rate (dashed line) in moderate training. Vertical line represents the
timing of devaluation. B. In extensive training. C. Probability of
actions in state \(S_0\) in moderate training. D. In extensive
training.}
\end{figure}

@@

We were able to qualitatively reproduce the first simulations of the
article. Despite the small differences in the exact timing of the
strategy shifting and in the probabilities of action, the behavior of
our implementation is similar to the original article. Thus, we confirm
the correctness of the model presented in the original article.
